---
title: "Exploratory Analysis"

output: html_document
---

### Introduction

We are interested in gathering statistics on video games for our final project. For most of the pandemic, video games were a way to escape and socialize with other players. They helped reduce stress and improve mental health during this time. Some related projects include an article posted by USA Today in 2021 and api based websites such as light.gg and lol.wiz that gathers statistics directly from games such as League of Legends and Destiny 2. We hope to answer questions about video game usage during the pandemic such as...

*"How has COVID changed video game sales and popularity?"*

*"How have video games impacted mental health during COVID?"*

*"How has COVID affected video game addiction?"*

### Part 1 - Summary Statistics

We decided to use the Games.csv dataset which consists of 175 observations. The most popular game was PlayerUnknown's Battlegorund, selling 42 million copies after its release in December of 2017. The least popular games solid only 1 million. 

### Part 2 - Aggregate Table

```{r aggregate_table, echo=FALSE, message=FALSE}
source("aggregate.r")
kable(genres_grouped_freq_df)
```

This table takes the dataset from game.csv and takes the genre columns to group the games by genre. It displays the 61 different genres and summarizes the number of games under each. For example, if there were 5 games in the action genre, it would display in the **"Genre"** column _"Action"_, with the number _5_ in the **"Total"** column next to it.


### Chart 1

```{r cloud, echo=FALSE, message=FALSE, warning=FALSE}
source("chart_1.r")
```

For Chart 1, we took the data from the Aggregate Table and produced a world cloud. It displays an easy to read visual where the genres with greater totals appear larger, and the less totalled ones appear smaller. We included genres with 3+ occurences, totalling 19 genres.  It gives us a wide range of data and allows us to see that _Action role-playing_ is the most popular genre.

### Chart 2

```{r genre_chart, echo=FALSE, message=FALSE, warning=FALSE}
source("chart_2.r")
plot(genre_play_time)
```

For this facet histogram,  we decided to look at the average time spend to complete the games of each genre. Each histogram represents one genre, the x axis is the _amount of time spent_ and the y axis the the _number of games_ that takes the given time to complete. By looking at each histogram, we can tell that most people prefer action games, as it has the highest amount. We can also tell that while sports is the second most played genre, it doesn't take as long to complete it. This could be because some sport games aren't made to be "completed", it's made so the player can experience the sport whenever they want, and stop whenever they want.

### Chart 3

```{r trendline, echo=FALSE, message=FALSE}
source("chart_3.r")
plot(genre_trendline)
```

For this line trend graph, we focused on how often each genre of games were searched on google with google trends. Since our group wanted to see the effects of COVID-19 on video games, we chose to begin from the start of 2019 (pre-Covid) to present time. Each line represents one genre, and from this graph, VR surpass all the other genres by a lot. we think this is because it is relatively new and more people are curious about it. It may also be due the Covid-19 pandemic, and the increased need for entertainment that didn't involve person to person contact. Virtual Reality games allow for an experience and movement similar to that of an outdoor activity, but within the confinment of your home. Other than that, it does match the data from chart 2, where actions games were still the most searched. Finally, we chose to omit the sports genre because the search for "sport games" on google usually means the actual physical ones like NBA or MLB.
