---
title: "Exploratory Analysis"

output: html_document
---

### Introduction

We are interested in gathering statistics on video games for our final project. For most of the pandemic, video games were a way to escape and socialize with other players. They helped reduce stress and improve mental health during this time. Some related projects include an article posted by USA Today in 2021 and api based websites such as light.gg and lol.wiz that gathers statistics directly from games such as League of Legends and Destiny 2. We hope to answer questions about video game usage during the pandemic such as...

*"How has COVID changed video game sales and popularity?"*

*"How have video games impacted mental health during COVID?"*

*"How has COVID affected video game addiction?"*

### Part 1 - Summary Statistics

We decided to use the Games.csv dataset which consists of 175 observations.

### Part 2 - Aggregate Table

```{r aggregate_table, echo=FALSE, message=FALSE}
source("aggregate.r")
kable(genres_grouped_freq_df)
```

### Chart 1

```{r cloud, echo=FALSE, message=FALSE, warning=FALSE}
source("chart_1.r")
```

### Chart 2

```{r genre_chart, echo=FALSE, message=FALSE, warning=FALSE}
source("chart_2.r")
plot(genre_play_time)
```

### Chart 3

```{r trendline, echo=FALSE, message=FALSE}
source("chart_3.r")
plot(genre_trendline)
```
